Simulations of Ballot Polling Risk-Limiting Audits

### 2021-11-01 MultipleRoundSims/sections/03-software.tex
Jupyter notebooks links

Using R2B2 is as simple as using any other Python library: simply import the library
and all of the functionality is at your finger tips. Not only does this allow users
to write their own Python scripts for exploring RLAs, it also allows R2B2 to be plugged
in to any other Python library. See the following Jupyter Notebooks for information on
the usage of R2B2:

\begin{itemize}
    \item \href{https://github.com/gwexploratoryaudits/r2b2/blob/notebooks/notebook/R2B2%20Basics.ipynb}{Basic Usage}
    \item \href{https://github.com/gwexploratoryaudits/r2b2/blob/notebooks/notebook/Generating%20Graphs.ipynb}{Generating Graphs}
\end{itemize}

>>>>

Using R2B2 is as simple as using any other Python library: simply import the library
and all of the functionality is at your finger tips. Not only does this allow users
to write their own Python scripts for exploring RLAs, it also allows R2B2 to be plugged
in to any other Python library. See the following Jupyter Notebooks for information on
the usage of R2B2: Basic Usage~\cite{jupyterBasic}, Generating Graphs~\cite{jupyterGraphs}.

% \begin{itemize} 
%     \item {Basic Usage} \cite{} % \href{https://github.com/gwexploratoryaudits/r2b2/blob/notebooks/notebook/R2B2%20Basics.ipynb}{Basic Usage}
%     \item \href{https://github.com/gwexploratoryaudits/r2b2/blob/notebooks/notebook/Generating%20Graphs.ipynb}{Generating Graphs}
% \end{itemize}
